Bootstrap with a grid

### 2024-07-24 Boot_grid.Rmd
Boot_grid without empty examples

---
title: "Bootstrap with a grid"
output:
  pdf_document: default
date: "2024-07-22"
---

@@

```{r}
cat("Monte Carlo variance:", res1_nb)
# Examples:
# Monte Carlo variance: 
```

@@

```{r}
cat("Mean of the variance of bootstrap samples:", res2_nb)
# Example:
# Mean of the variance of bootstrap samples: 
```

```{r}
cat("We get a difference of: ", 100*(max(res1_nb,res2_nb)-min(res1_nb,res2_nb))/min(res1_nb,res2_nb), "%", sep = "")
# Example:
# We get a difference of: 
```

@@

```{r}
cat("Monte Carlo variance:", res1_vol)
# Ex:
# Monte Carlo variance: 
```

@@

```{r}
cat("Mean of the variance of bootstrap samples:", res2_vol)
# Ex:
# Mean of the variance of bootstrap samples: 
```

```{r}
cat("We get a difference of: ", 100*(max(res1_vol,res2_vol)-min(res1_vol,res2_vol))/min(res1_vol,res2_vol), "%", sep = "")
# Ex:
# We get a difference of: 
```

>>>>

---
title: "Bootstrap with a grid"
output:
  pdf_document: default
date: "2024-07-23"
---

@@

```{r}
cat("Monte Carlo variance:", res1_nb)
```

@@

```{r}
cat("Mean of the variance of bootstrap samples:", res2_nb)
```

```{r}
cat("We get a difference of: ", 100*(max(res1_nb,res2_nb)-min(res1_nb,res2_nb))/min(res1_nb,res2_nb), "%", sep = "")
```

@@

```{r}
cat("Monte Carlo variance:", res1_vol)
```

@@

```{r}
cat("Mean of the variance of bootstrap samples:", res2_vol)
```

```{r}
cat("We get a difference of: ", 100*(max(res1_vol,res2_vol)-min(res1_vol,res2_vol))/min(res1_vol,res2_vol), "%", sep = "")
```
